---
title: "MEV_analysis_script"
author: "Leopold Roth"
date: "2024-03-05"
output: 
  html_document:
    toc: true
    toc_depth: 3
    number_sections: true
    theme: united
    toc_float: true
---

# packages

```{r message=FALSE, warning=FALSE}
library(dplyr)
library(readr)
library(ggplot2)
library(psych)
library(lavaan)
library(easystats)
library(semPlot)
library(reshape2)
library(misty)
library(foreign)
library(varhandle)
library(car)
library(eRm)
library(tidyr)
library(haven)
library(BayesFactor)
library(stringr)
library(patchwork)
```

# TODOs
add here, if something comes up

# source functions from script
this 'runs' the script functions_run_first.R and saves work to do it yourself/otherwise can't knit (create markdown)
```{r, include=FALSE}
source("functions_run_first.R", local = knitr::knit_global())
```

#load data

```{r}
df_ge <- read_csv("testdata/testdata_mev_GE.csv") #Germany
df_me <- read_csv("testdata/testdata_mev_ME.csv") #Mexico
```

# apply exclusion criteria
- didnt complete survey
- language level < very good (x)
- not resident in target country (x)
- missed one of the two attention checks
- too fast completion (> 3SD from mean)
```{r}
#apply data cleaning function (CURRENTLY DEACTIVATED; BECAUSE RESPONSES ARE RANDOM)
# df_ge <- clean_data(df_ge)
# df_me <- clean_data(df_me)
```

# prepare data
## renaming and means

```{r}
#apply to dataframes
df_ge <- preparation(df_ge)
df_me <- preparation(df_me)
```

## create differences scores (exclude by effort)
this also filters out participants who thought that the low effort condition was more/equally effortful than the high effort condition
```{r}
#apply function to dataframes
df_ge <- difference_scores(df_ge)
df_me <- difference_scores(df_me)
```

# reliabilities
## core goodness
### low effort

```{r}
#alpha
psych::alpha(df_ge %>% select(c(Ch_LoEf_3, Ch_LoEf_9, Ch_LoEf_11, Ch_LoEf_10, Ch_LoEf_13, Ch_LoEf_14
)))[[1]]
psych::alpha(df_me %>% select(c(Ch_LoEf_3, Ch_LoEf_9, Ch_LoEf_11, Ch_LoEf_10, Ch_LoEf_13, Ch_LoEf_14
)))[[1]]
#omega
psych::omega(df_ge %>% select(c(Ch_LoEf_3, Ch_LoEf_9, Ch_LoEf_11, Ch_LoEf_10, Ch_LoEf_13, Ch_LoEf_14
)))[[1]]
psych::omega(df_me %>% select(c(Ch_LoEf_3, Ch_LoEf_9, Ch_LoEf_11, Ch_LoEf_10, Ch_LoEf_13, Ch_LoEf_14
)))[[1]]
```

### high effort

```{r}
#alpha
psych::alpha(df_ge %>% select(c(Ch_HiEf_3, Ch_HiEf_9, Ch_HiEf_11, Ch_HiEf_10, Ch_HiEf_13, Ch_HiEf_14
)))[[1]]
psych::alpha(df_me %>% select(c(Ch_HiEf_3, Ch_HiEf_9, Ch_HiEf_11, Ch_HiEf_10, Ch_HiEf_13, Ch_HiEf_14
)))[[1]]
#omega
psych::omega(df_ge %>% select(c(Ch_HiEf_3, Ch_HiEf_9, Ch_HiEf_11, Ch_HiEf_10, Ch_HiEf_13, Ch_HiEf_14
)))[[1]]
psych::omega(df_me %>% select(c(Ch_HiEf_3, Ch_HiEf_9, Ch_HiEf_11, Ch_HiEf_10, Ch_HiEf_13, Ch_HiEf_14
)))[[1]]
```

## value commitment
### low effort

```{r}
#alpha
psych::alpha(df_ge %>% select(c(Ch_LoEf_1, Ch_LoEf_5, Ch_LoEf_15, Ch_LoEf_8, Ch_LoEf_4, Ch_LoEf_12, Ch_LoEf_7)))[[1]]
psych::alpha(df_me %>% select(c(Ch_LoEf_1, Ch_LoEf_5, Ch_LoEf_15, Ch_LoEf_8, Ch_LoEf_4, Ch_LoEf_12, Ch_LoEf_7)))[[1]]
#omega
psych::omega(df_ge %>% select(c(Ch_LoEf_1, Ch_LoEf_5, Ch_LoEf_15, Ch_LoEf_8, Ch_LoEf_4, Ch_LoEf_12, Ch_LoEf_7)))[[1]]
psych::omega(df_me %>% select(c(Ch_LoEf_1, Ch_LoEf_5, Ch_LoEf_15, Ch_LoEf_8, Ch_LoEf_4, Ch_LoEf_12, Ch_LoEf_7)))[[1]]
```

### high effort

```{r}
#alpha
psych::alpha(df_ge %>% select(c(Ch_HiEf_1, Ch_HiEf_5, Ch_HiEf_15, Ch_HiEf_8, Ch_HiEf_4, Ch_HiEf_12, Ch_HiEf_7)))[[1]]
psych::alpha(df_me %>% select(c(Ch_HiEf_1, Ch_HiEf_5, Ch_HiEf_15, Ch_HiEf_8, Ch_HiEf_4, Ch_HiEf_12, Ch_HiEf_7)))[[1]]
#omega
psych::omega(df_ge %>% select(c(Ch_HiEf_1, Ch_HiEf_5, Ch_HiEf_15, Ch_HiEf_8, Ch_HiEf_4, Ch_HiEf_12, Ch_HiEf_7)))[[1]]
psych::omega(df_me %>% select(c(Ch_HiEf_1, Ch_HiEf_5, Ch_HiEf_15, Ch_HiEf_8, Ch_HiEf_4, Ch_HiEf_12, Ch_HiEf_7)))[[1]]
```

# prepare analysis
## keep needed columns

```{r}
#apply function to dataframes
df_ge <- reduction(df_ge)
df_me <- reduction(df_me)
```

## add country ID and create overall df

```{r}
#country ID
df_ge$country <- rep("GE",nrow(df_ge))
df_me$country <- rep("ME",nrow(df_me))

df_all <- rbind(df_ge,df_me)
```

## demographic analysis

```{r}
#Age
psych::describe(df_ge$Age)
psych::describe(df_me$Age)
psych::describe(df_all$Age)

#Gender
table(df_ge$Gen)
table(df_me$Gen)
table(df_all$Gen)
```

## descriptive: means
get all descriptives of everything and filter for what is needed
```{r}
means_all <- rownames_as_column(psych::describe(df_all))
means_ge <- rownames_as_column(psych::describe(df_ge))
means_me <- rownames_as_column(psych::describe(df_me))
```

# main analysis
## comparisons: core goodness

```{r}
#all
cg_all <- as.data.frame(report::report(t.test(df_all$core_good_lo, df_all$core_good_he, paired = TRUE))) #this computes the paired t-test and saves the results as dataframe
cg_all <- cg_all %>% select(p, Cohens_d, Cohens_d_CI_low, Cohens_d_CI_high) #this extracts the metrices of interest and binds them together
cg_all$BF <- as.data.frame(ttestBF(x = df_all$core_good_lo, y = df_all$core_good_he, paired = TRUE))[[1]] #this computes the Bayes Factor of the test and binds it to the other data; this is done for all tests in the same manner

#Germany
cg_ge <- as.data.frame(report::report(t.test(df_ge$core_good_lo, df_ge$core_good_he, paired = TRUE)))
cg_ge <- cg_ge %>% select(p, Cohens_d, Cohens_d_CI_low, Cohens_d_CI_high)
cg_ge$BF <- as.data.frame(ttestBF(x = df_ge$core_good_lo, y = df_ge$core_good_he, paired = TRUE))[[1]]

#Mexico
cg_me <- as.data.frame(report::report(t.test(df_me$core_good_lo, df_me$core_good_he, paired = TRUE)))
cg_me <- cg_me %>% select(p, Cohens_d, Cohens_d_CI_low, Cohens_d_CI_high)
cg_me$BF <- as.data.frame(ttestBF(x = df_me$core_good_lo, y = df_me$core_good_he, paired = TRUE))[[1]]

#combine results
cg_results <- bind_rows(cg_all, cg_ge, cg_me) #using more flexible dplyr function; rbind had trouble with row.names
cg_results$target <- rep("core_goodness",nrow(cg_results)) #add column to mention DV
rm(list=c("cg_all","cg_ge","cg_me")) #removes non-needed dfs
```

## comparisons: value commitment

```{r}
#all
vc_all <- as.data.frame(report::report(t.test(df_all$value_comm_lo, df_all$value_comm_he, paired = TRUE)))
vc_all <- vc_all %>% select(p, Cohens_d, Cohens_d_CI_low, Cohens_d_CI_high)
vc_all$BF <- as.data.frame(ttestBF(x = df_all$value_comm_lo, y = df_all$value_comm_he, paired = TRUE))[[1]]

#Germany
vc_ge <- as.data.frame(report::report(t.test(df_ge$value_comm_lo, df_ge$value_comm_he, paired = TRUE)))
vc_ge <- vc_ge %>% select(p, Cohens_d, Cohens_d_CI_low, Cohens_d_CI_high)
vc_ge$BF <- as.data.frame(ttestBF(x = df_ge$value_comm_lo, y = df_ge$value_comm_he, paired = TRUE))[[1]]

#Mexico
vc_me <- as.data.frame(report::report(t.test(df_me$value_comm_lo, df_me$value_comm_he, paired = TRUE)))
vc_me <- vc_me %>% select(p, Cohens_d, Cohens_d_CI_low, Cohens_d_CI_high)
vc_me$BF <- as.data.frame(ttestBF(x = df_me$value_comm_lo, y = df_me$value_comm_he, paired = TRUE))[[1]]

#combine results
vc_results <- bind_rows(vc_all, vc_ge, vc_me)
vc_results$target <- rep("value_commitment",nrow(vc_results)) #add column to mention DV
rm(list=c("vc_all","vc_ge","vc_me")) #removes non-needed dfs
```

## comparisons: pay deservingness

```{r}
#all
pd_all <- as.data.frame(report::report(t.test(df_all$pay_deservingness_lo, df_all$pay_deservingness_he, paired = TRUE)))
pd_all <- pd_all %>% select(p, Cohens_d, Cohens_d_CI_low, Cohens_d_CI_high)
pd_all$BF <- as.data.frame(ttestBF(x = df_all$pay_deservingness_lo, y = df_all$pay_deservingness_he, paired = TRUE))[[1]]

#Germany
pd_ge <- as.data.frame(report::report(t.test(df_ge$pay_deservingness_lo, df_ge$pay_deservingness_he, paired = TRUE)))
pd_ge <- pd_ge %>% select(p, Cohens_d, Cohens_d_CI_low, Cohens_d_CI_high)
pd_ge$BF <- as.data.frame(ttestBF(x = df_ge$pay_deservingness_lo, y = df_ge$pay_deservingness_he, paired = TRUE))[[1]]

#Mexico
pd_me <- as.data.frame(report::report(t.test(df_me$pay_deservingness_lo, df_me$pay_deservingness_he, paired = TRUE)))
pd_me <- pd_me %>% select(p, Cohens_d, Cohens_d_CI_low, Cohens_d_CI_high)
pd_me$BF <- as.data.frame(ttestBF(x = df_me$pay_deservingness_lo, y = df_me$pay_deservingness_he, paired = TRUE))[[1]]

#combine results
pd_results <- bind_rows(pd_all, pd_ge, pd_me)
pd_results$target <- rep("pay_deservingness",nrow(pd_results)) #add column to mention DV
rm(list=c("pd_all","pd_ge","pd_me")) #removes non-needed dfs
```

## comparisons: warmth

```{r}
#all
wa_all <- as.data.frame(report::report(t.test(df_all$warmth_lo, df_all$warmth_he, paired = TRUE)))
wa_all <- wa_all %>% select(p, Cohens_d, Cohens_d_CI_low, Cohens_d_CI_high)
wa_all$BF <- as.data.frame(ttestBF(x = df_all$warmth_lo, y = df_all$warmth_he, paired = TRUE))[[1]]

#Germany
wa_ge <- as.data.frame(report::report(t.test(df_ge$warmth_lo, df_ge$warmth_he, paired = TRUE)))
wa_ge <- wa_ge %>% select(p, Cohens_d, Cohens_d_CI_low, Cohens_d_CI_high)
wa_ge$BF <- as.data.frame(ttestBF(x = df_ge$warmth_lo, y = df_ge$warmth_he, paired = TRUE))[[1]]

#Mexico
wa_me <- as.data.frame(report::report(t.test(df_me$warmth_lo, df_me$warmth_he, paired = TRUE)))
wa_me <- wa_me %>% select(p, Cohens_d, Cohens_d_CI_low, Cohens_d_CI_high)
wa_me$BF <- as.data.frame(ttestBF(x = df_me$warmth_lo, y = df_me$warmth_he, paired = TRUE))[[1]]

#combine results
wa_results <- bind_rows(wa_all, wa_ge, wa_me)
wa_results$target <- rep("warmth",nrow(wa_results)) #add column to mention DV
rm(list=c("wa_all","wa_ge","wa_me")) #removes non-needed dfs
```

## comparisons: competence

```{r}
#all
co_all <- as.data.frame(report::report(t.test(df_all$competence_lo, df_all$competence_he, paired = TRUE)))
co_all <- co_all %>% select(p, Cohens_d, Cohens_d_CI_low, Cohens_d_CI_high)
co_all$BF <- as.data.frame(ttestBF(x = df_all$competence_lo, y = df_all$competence_he, paired = TRUE))[[1]]

#Germany
co_ge <- as.data.frame(report::report(t.test(df_ge$competence_lo, df_ge$competence_he, paired = TRUE)))
co_ge <- co_ge %>% select(p, Cohens_d, Cohens_d_CI_low, Cohens_d_CI_high)
co_ge$BF <- as.data.frame(ttestBF(x = df_ge$competence_lo, y = df_ge$competence_he, paired = TRUE))[[1]]

#Mexico
co_me <- as.data.frame(report::report(t.test(df_me$competence_lo, df_me$competence_he, paired = TRUE)))
co_me <- co_me %>% select(p, Cohens_d, Cohens_d_CI_low, Cohens_d_CI_high)
co_me$BF <- as.data.frame(ttestBF(x = df_me$competence_lo, y = df_me$competence_he, paired = TRUE))[[1]]

#combine results
co_results <- bind_rows(co_all, co_ge, co_me)
co_results$target <- rep("competence",nrow(co_results)) #add column to mention DV
rm(list=c("co_all","co_ge","co_me")) #removes non-needed dfs
```

### combine t-test results

```{r}
#combine results
comp_results <- bind_rows(cg_results,
                      vc_results,
                      pd_results,
                      wa_results,
                      co_results)

#add names list
samples <- c("global","germany","mexico")
comp_results$countries <- rep(samples,5)

#log-transform BFs
comp_results$BF <- log(comp_results$BF)

comp_results <- comp_results %>% #rounds all numeric variables to 3 decimals
  mutate_if(is.numeric, round, digits = 3)

#this makes the transfer to word easier
##open excel, find/replace comma with point, copy, paste, correct format
#writexl::write_xlsx(comp_results, "t-results.xlsx")

#remove non-needed objects
rm(list = c("cg_results","vc_results","pd_results","wa_results","co_results","samples"))
```

## ease extraction of means and sds

```{r}
#combine and extract means (sds) for tables
df_list <- list(means_all, means_ge,means_me) # Example list of dataframes

target_rows <- c(9, 18, #rows of interest
                 10, 19,
                 8, 17,
                 2, 11,
                 3, 12)

# Initialize an empty dataframe to store the combined results
combined_rows <- data.frame()

# Loop through each target row index
for(row_index in target_rows) {
  # Extract and combine the rows for the current index from all dataframes
  combined_rows <- rbind(combined_rows, extract_and_combine_rows(df_list, row_index))
}

combined_rows <- combined_rows %>% 
  select(rowname,mean,sd) %>% #keep only needed columns
  mutate(mean_sd = paste0(round(mean, 2), " (", round(sd, 2), ")")) %>% #round and combine in mean(sd) format
  select(rowname,mean_sd) #select only needed columns

#writexl::write_xlsx(combined_rows, "means_t-results.xlsx")
```

## beeswarm plot

```{r}
df_plot <- df_all #define df for plotting

df_plot <- df_plot %>% #recode country for readbility
  mutate(country = case_when(
    country == "GE" ~ "Germany",
    country == "ME" ~ "Mexico",
    TRUE ~ country  # Default case to keep original values for other countries
  ))

#apply function for restructuring and plotting data
plot_cg <- plot_violin_with_means(df_plot, c("core_good_lo", "core_good_he"), "core goodness")

plot_vc <- plot_violin_with_means(df_plot, c("value_comm_lo", "value_comm_he"), "value commitment")

plot_pd <- plot_violin_with_means(df_plot, c("pay_deservingness_lo", "pay_deservingness_he"),"pay deservingness")

plot_wa <- plot_violin_with_means(df_plot, c("warmth_lo", "warmth_he"), "warmth")

plot_co <- plot_violin_with_means(df_plot, c("competence_lo", "competence_he"), "competence")

combined_plot <- plot_cg / plot_vc / plot_pd / plot_wa / plot_co #combine plots

#ggsave("combined_plot.png", combined_plot, width = 10, height = 12, dpi = 300)
```

## predictions: core goodness

```{r}
#global samples
m0 <- lm(core_good_diff ~ 1, data = df_all)
m1 <- lm(core_good_diff ~ Age, data = df_all)
m2 <- lm(core_good_diff ~ poly(Age,2,raw=TRUE), data = df_all)

sjPlot::tab_model(m0,m1,m2, show.std = TRUE)

bf1 <- performance::test_bf(m0, m1) #BF linear vs. null model
bf2 <- performance::test_bf(m1, m2) #BF quadratic vs linear model

log(bf1[[3]])
log(bf2[[3]])

#germany
m0 <- lm(core_good_diff ~ 1, data = df_ge)
m1 <- lm(core_good_diff ~ Age, data = df_ge)
m2 <- lm(core_good_diff ~ poly(Age,2,raw=TRUE), data = df_ge)

sjPlot::tab_model(m0,m1,m2, show.std = TRUE)

bf1 <- performance::test_bf(m0, m1) #BF linear vs. null model
bf2 <- performance::test_bf(m1, m2) #BF quadratic vs linear model

log(bf1[[3]])
log(bf2[[3]])

#mexico
m0 <- lm(core_good_diff ~ 1, data = df_me)
m1 <- lm(core_good_diff ~ Age, data = df_me)
m2 <- lm(core_good_diff ~ poly(Age,2,raw=TRUE), data = df_me)

sjPlot::tab_model(m0,m1,m2, show.std = TRUE)

bf1 <- performance::test_bf(m0, m1) #BF linear vs. null model
bf2 <- performance::test_bf(m1, m2) #BF quadratic vs linear model

log(bf1[[3]])
log(bf2[[3]])
```

## predictions: value commitment

```{r}
#global samples
m0 <- lm(value_comm_diff ~ 1, data = df_all)
m1 <- lm(value_comm_diff ~ Age, data = df_all)
m2 <- lm(value_comm_diff ~ poly(Age,2,raw=TRUE), data = df_all)

sjPlot::tab_model(m0,m1,m2, show.std = TRUE)

bf1 <- performance::test_bf(m0, m1) #BF linear vs. null model
bf2 <- performance::test_bf(m1, m2) #BF quadratic vs linear model

log(bf1[[3]])
log(bf2[[3]])

#germany
m0 <- lm(value_comm_diff ~ 1, data = df_ge)
m1 <- lm(value_comm_diff ~ Age, data = df_ge)
m2 <- lm(value_comm_diff ~ poly(Age,2,raw=TRUE), data = df_ge)

sjPlot::tab_model(m0,m1,m2, show.std = TRUE)

bf1 <- performance::test_bf(m0, m1) #BF linear vs. null model
bf2 <- performance::test_bf(m1, m2) #BF quadratic vs linear model

log(bf1[[3]])
log(bf2[[3]])

#mexico
m0 <- lm(value_comm_diff ~ 1, data = df_me)
m1 <- lm(value_comm_diff ~ Age, data = df_me)
m2 <- lm(value_comm_diff ~ poly(Age,2,raw=TRUE), data = df_me)

sjPlot::tab_model(m0,m1,m2, show.std = TRUE)

bf1 <- performance::test_bf(m0, m1) #BF linear vs. null model
bf2 <- performance::test_bf(m1, m2) #BF quadratic vs linear model

log(bf1[[3]])
log(bf2[[3]])
```

## exploratory multi-level model

```{r}
#define country as factor
df_all$country <- as.factor(df_all$country)

#core goodness

m0 <- lme4::lmer(core_good_diff ~ 1 + (1+Age|country), data = df_all)
m1 <- lme4::lmer(core_good_diff ~ country * Age + (1+Age|country), data = df_all)
m2 <- lme4::lmer(core_good_diff ~ country * poly(Age,2,raw=TRUE) + (1+Age|country), data = df_all)

sjPlot::tab_model(m0,m1,m2, show.std = TRUE)
sjPlot::plot_model(m2)

performance::test_bf(m0, m1) #BF linear vs. null model
performance::test_bf(m1, m2) #BF quadratic vs linear model

#value commitment

m0 <- lme4::lmer(value_comm_diff ~ 1 + (1+Age|country), data = df_all)
m1 <- lme4::lmer(value_comm_diff ~ country * Age + (1+Age|country), data = df_all)
m2 <- lme4::lmer(value_comm_diff ~ country * poly(Age,2,raw=TRUE) + (1+Age|country), data = df_all)

sjPlot::tab_model(m0,m1,m2, show.std = TRUE)
sjPlot::plot_model(m2)

performance::test_bf(m0, m1) #BF linear vs. null model
performance::test_bf(m1, m2) #BF quadratic vs linear model
```

## manipulation checks

```{r}
# do people see quality, difficulty and value of work differently
## quality
quality <- as.data.frame(report::report(t.test(df_all$quality_lo, df_all$quality_he, paired = TRUE)))
quality <- quality %>% select(p, Cohens_d, Cohens_d_CI_low, Cohens_d_CI_high)
quality$BF <- as.data.frame(ttestBF(x = df_all$quality_lo, y = df_all$quality_he, paired = TRUE))[[1]]

## difficulty
difficulty <- as.data.frame(report::report(t.test(df_all$difficulty_lo, df_all$difficulty_he, paired = TRUE)))
difficulty <- difficulty %>% select(p, Cohens_d, Cohens_d_CI_low, Cohens_d_CI_high)
difficulty$BF <- as.data.frame(ttestBF(x = df_all$difficulty_lo, y = df_all$difficulty_he, paired = TRUE))[[1]]

##value
valuable <- as.data.frame(report::report(t.test(df_all$valuable_lo, df_all$valuable_he, paired = TRUE)))
valuable <- valuable %>% select(p, Cohens_d, Cohens_d_CI_low, Cohens_d_CI_high)
valuable$BF <- as.data.frame(ttestBF(x = df_all$valuable_lo, y = df_all$valuable_he, paired = TRUE))[[1]]

name_check <- c("quality", "difficulty", "value")

checks <- rbind(quality, difficulty, valuable)

checks$dimensions <- name_check

checks <- checks %>%
    mutate_if(is.numeric, round, digits = 3)
```



